### 2024-01-02 chapters/background.tex
Minor edits and polishing

\section{Variational autoencoders}
%
% \paragraph{Deep generative models} 
Variational autoencoders (VAEs) belong to the class of deep generative models. 
These are models that use deep neural networks to approximate the underlying distribution of the unlabeled training data, from which they can then be used to generate new data samples. 
% These are models that unsupervisedly learn a representation of data and can be used to generate new samples by learning an approximation to the distribution that generated the training data. 
There exist at least six main classes of deep generative models: variational autoencoders \parencite{kingma_autoencoding_2014,rezende_stochastic_2014,ranganath_hierarchical_2016,vahdat_nvae_2020,child_very_2021}, normalizing flow models \parencite{dinh_nice_2015,rezende_variational_2015,dinh_density_2017,kingma_glow_2018,grathwohl_ffjord_2018}, diffusion models \parencite{sohl-dickstein_deep_2015,song_generative_2019, ho_denoising_2020, vahdat_scorebased_2021}, energy-based models \parencite{lecun_tutorial_2006,hinton_fast_2006,salakhutdinov_efficient_2010,du_implicit_2019}, autoregressive models \parencite{oord_conditional_2016,oord_wavenet_2016,radford_improving_2018}, and generative adversarial networks \parencite{goodfellow_generative_2014,arjovsky_wasserstein_2017,brock_large_2019,karras_stylebased_2019}.

@@

\subsection{Variational inference} \label{sec:variational-autoencoders}
To model high-dimensional data, we want to use neural networks to represent the generative process. 
This leads to deep latent variable models which were pioneered by \textcite{kingma_autoencoding_2014,rezende_stochastic_2014}. The authors propose to factor the joint distribution and parameterize it using a neural network with parameters $\thetab$ and let $p_\thetab(\xb,\zb) = p_\thetab(\xb|\zb)p(\zb)$ where $p(\zb)$ is a prior.

>>>>

\section{Variational autoencoders}\label{sec:variational-autoencoders}
%
% \paragraph{Deep generative models} 
Variational autoencoders (VAEs) belong to the class of deep generative models. 
These are models that use deep neural networks to approximate the underlying distribution of the unlabeled training data, from which they can then be used to generate new data samples. 
% These are models that unsupervisedly learn a representation of data and can be used to generate new samples by learning an approximation to the distribution that generated the training data. 
There exist at least six main classes of deep generative models: variational autoencoders \parencite{kingma_autoencoding_2014,rezende_stochastic_2014,ranganath_hierarchical_2016,vahdat_nvae_2020,child_very_2021}, normalizing flow models \parencite{dinh_nice_2015,rezende_variational_2015,dinh_density_2017,kingma_glow_2018,grathwohl_ffjord_2018}, diffusion models \parencite{sohl-dickstein_deep_2015,song_generative_2019, ho_denoising_2020, vahdat_scorebased_2021}, energy-based models \parencite{lecun_tutorial_2006,hinton_fast_2006,salakhutdinov_efficient_2010,du_implicit_2019}, autoregressive models \parencite{oord_conditional_2016,oord_wavenet_2016,radford_improving_2018}, and generative adversarial networks \parencite{goodfellow_generative_2014,arjovsky_wasserstein_2017,brock_large_2019,karras_stylebased_2019}.

@@

\subsection{Variational inference}
To model high-dimensional data, we want to use neural networks to represent the generative process. 
This leads to deep latent variable models which were pioneered by \textcite{kingma_autoencoding_2014,rezende_stochastic_2014}. The authors propose to factor the joint distribution and parameterize it using a neural network with parameters $\thetab$ and let $p_\thetab(\xb,\zb) = p_\thetab(\xb|\zb)p(\zb)$ where $p(\zb)$ is a prior.

### 2024-01-02 frontmatter/acknowledgements.tex
Minor edits and polishing

\chapter[acknowledgements]{Acknowledgements}
First, I want to thank my supervisors. Jes, you have been an amazing support through this project. 
Your positivity and insightfulness were essential to me daring to take on this project, and to its success. 
Lars, you have been an indispensable source of purpose, energy, and direction. I look forward to many more fruitful discussions in the future.

@@

I want to thank Lars, Andreas, and Michael for letting me become part of the Corti project after graduating back in 2018. 
The foundational will to invest and believe in people, and to dare to have bold visions, has made Corti a fantastic place for me to develop, professionally and personally. 
I want to also thank the members of the machine learning team during the first years of my time at Corti. Lasse, Tycho, Marco, Jan, Janek, and Joakim, you all played a part in inspiring and enabling me to dive into this project. 
A special thanks should go to Joakim. Your honest curiosity and dedication has been a wonderful addition to the research team. 
Finally, I want to thank Lasse. Our numerous inspirational discussions and combined efforts through the years have been instrumental in shaping the trajectory of this thesis. It has been a privilege to carry out this PhD project in the company of you both.

I want to also thank my friends and my family who have provided much needed diversion throughout the years. 
Last, but not least, I want to thank my wife, Rikke, who has been an unbelievably patient and absolutely indispensable supporter at every step of this undertaking.

>>>>

\chapter[acknowledgements]{Acknowledgements}
First, I want to thank my supervisors. Jes, you have been an amazing support through this project. 
Your positivity and insightfulness were essential to me daring to take on this project, and to its success. 
Lars, you have been a completely indispensable source of purpose, energy, and direction throughout my time with Corti. I look forward to many more fruitful discussions in the future.

@@

I want to thank Lars, Andreas, and Michael for letting me become part of the Corti project after graduating back in 2018. 
The foundational will to invest and believe in people, and to dare to have bold visions, has made Corti a fantastic place for me to develop, professionally and personally. 
I want to also thank the members of the machine learning team during the first years of my time at Corti. Lasse, Tycho, Marco, Jan, Janek, and Joakim, you all played a part in inspiring and enabling me to dive into this project. 
A special thanks should go to Joakim. Your honest curiosity and dedication has been a wonderful addition to the research team. 
I also want to thank Lasse. The numerous inspirational discussions with you and our combined efforts through the years have been instrumental in shaping this thesis. It has been a privilege to carry out this PhD project in the company of you both.

I want to also thank my friends and my family who have provided much needed diversion and encouragement throughout the years. 
Last, but not least, I want to thank my wife, Rikke, who has been an unbelievably patient and absolutely essential supporter at every step of this undertaking. I am excited about what lies ahead for us and our daughter Vigga, and I cannot wait to build our future together.

### 2024-01-02 preamble/etc.tex
Make project run in VS Code
Sync-up
Add benchmarking paper
Add review paper (WIP)
Minor updates
Updates
Work on variational autoencoders
Minor edits and polishing

\usepackage{blindtext}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{multicol}
\usepackage{booktabs}
\usepackage{multirow}
\usepackage{enumerate}
\usepackage{enumitem}
\usepackage{layouts}
\usepackage[showframe=\showframe,xetex]{geometry}

%\usepackage{pgfplots}                 % Plot tools
%\pgfplotsset{compat=1.7}
\usetikzlibrary{
    arrows,
    matrix,
    positioning,
    shapes,
    topaths,
    bayesnet,
}

>>>>

\usepackage{blindtext}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{multicol}
\usepackage{multirow}
\usepackage{makecell}
\usepackage{booktabs}
\usepackage{enumerate}
\usepackage{enumitem}
% \usepackage{layouts}
\usepackage[showframe=\showframe,xetex]{geometry}
\usepackage{adjustbox}
\usepackage{siunitx}
\usepackage{nomencl}
\usepackage[acronym,toc]{glossaries}

% Hyphenation
\hyphenation{ma-skin-læ-rings-mo-del}
\hyphenation{ma-skin-læ-rings-mo-del-ler}
\hyphenation{ty-pi-ka-li-tets-tests}
\hyphenation{ta-le-re-præ-sen-ta-tions-model-ler}
\hyphenation{me-to-de}
\hyphenation{me-di-cin-ske}

\DeclareMathOperator*{\argmax}{arg\,max}
\DeclareMathOperator*{\argmin}{arg\,min}

%\usepackage{pgfplots}                 % Plot tools
%\pgfplotsset{compat=1.7}
\usetikzlibrary{
    arrows,
    matrix,
    positioning,
    shapes,
    shapes.multipart,
    topaths,
    bayesnet,
}
\input{preamble/bayesnet_extras}

\definecolor{customgreen} {RGB}{217	234	212}
\definecolor{customblue}  {RGB}{205	226	242}
\definecolor{custommorered}{RGB}{218 46 42}
\definecolor{customred}{RGB}{255 182 173}%{255 149 150}

\colorlet{observed-color}{customgreen}
\colorlet{latent-color}{customblue}
\colorlet{deterministic-color}{gray!15}
\colorlet{deterministic-skip-color}{custommorered}
\colorlet{shared-function-color}{blue}
